TAPIR: Threaded Application Programming on Intermittent Resources

### 2017-05-11 paper.tex
conclusion

\section{Conclusion}
Multithreading in intermittence {\em is} a good idea!

>>>>

\section{Conclusion}
The increased prevalence of IoT devices necessitates an increased ability to 
run larger, general purpose applications on devices with smaller memory and
energy footprints. With the increased research on intermittently powered devices
for use in the embedded sphere, it is a logical next step to explore the use 
of general purpose threaded code on an intermittent device. We have shown
through the design and implementation of TAPIR on top of the Chain intermittent
programming model that adding functionality for multiprogramming with
multithreaded applications can have a low enough memory and power overhead to be
considered useful on such a device. Additionally, we have implemented a safe
locking structure for use in nonvolatile memory for such applications that 
maintains RMW restrictions in the intermittent execution model and allows
for larger shared data structures without the overhead of memory duplication
that may overcrowd a small device. We have shown with this design that threaded
applications can be programmed in a familiar way to software designers and that
it is a viable next step in intermittent device research.
